\documentclass[a4paper,12pt]{article}
\author{Gabriel Elkind}
\title{COMP312 - Assignment 2}
\date{\today}

\begin{document}

\maketitle

\begin{enumerate}

\item Show how to multiply the complex numbers $a + bi$ and $c + di$ using only three
multiplications of real numbers.
    

\item Give asymptotic upper and lower bounds for $T(n)$ in each of the following recur-
rences.
\begin{enumerate}
    \item $T(n)=4T(n/3)+n \lg n$
    \item(c) $T(n)=4T(n/2)+n^2\sqrt{n}$
    \item(f) $T(n)=T(n/2)+T(n/4)+T(n/8)+n$
    \item(h) $T(n)=T(n-1)+\lg n$ 
\end{enumerate}

\item Let $X[1...n]$ and $Y[1...n]$ be two arrays, each containing $n$ numbers already in sorted order. Give an $O(\lg n)$-time algorithm to find the median of all $2n$ elements in arrays $X$ and $Y$ 

\item Express the running time (as a function of the length of y only, i.e., assume that x is fixed for this analysis and compute the asymptotic running time as the length of y increases) of the following pseudo-code algorithm as a recurrence and solve it. What does the algorithm do?

\begin{verbatim}
    M(x,y):
    if y=0 return 0 else
    return M(2x,floorof(y/2))+x(ymod2)
\end{verbatim}

\item
\begin{verbatim}
    Stooge-sort(A,i,j)
    begin
        if A[i] > A[j] then
            swap A[i] and A[j]
        if i + 1 >= j then
            return k = floor((j - i + 1)/3)
        Stooge-sort(A,i,j-k)    Comment: Sort first two-thirds.
        Stooge-sort(A,i+k,j)    Comment: Sort last two-thirds.
        Stooge-sort(A,i,j-k)    Comment:Sort first two-thirds again!
\end{verbatim}
\begin{enumerate}
    \item Give an informal but convincing explanation (not a rigorous proof by induction) of why the approach of sorting the first two-thirds of the array, then sorting the last two-thirds of the array, and then sorting again the first two-thirds of the array yields a sorted array.
    \item Find a recurrence for the worst-case running time of Stooge-sort.
    \item Next, solve the recurrence using the recursion-tree method. 
    \item How does the worst-case running time of Stooge-Sort compare with the worst- case running times of other sorting algorithms (Insertion sort, Selection sort, Mergesort, Quicksort, Bubblesort, Heapsort)?



\end{enumerate}

\end{enumerate}

\end{document}

